Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
fixed the todos

74.43\% of the builds in the reduced dataset were successful, and thus a naive
classifer that always guesses ``successful'' would succeed 74.43\% of the time.
To penalize misclassification for
both classes equally, we created a second balanced dataset by randomly 
sub-sampling the successful builds until the two build status were
equal, a process known as downsampling.  We train on the down-sampled data but show results on both 
downsampled and non-downsampled data sets.\todo{CLG says: that last sentence is
  true, right?}

\section{Evaluation}
\begin{table*}[ht]
\centering
\begin{tabular}{l||r|r||r|r}
  & \multicolumn{2}{|c||}{Non-Downsampled}  & \multicolumn{2}{|c}{Downsampled} \\
\hline
  & Technical & Technical and Social & Technical & Technical and Social \\
\hline
\textbf{Correctly Classified Instances}&  77.01\% & 81.10\%  & 64.10\% & 76.09\%\\

@@

%\paragraph{External validity} 
Our results might not generalize to 
 other instances outside of the studied cases.  To mitigate this risk, we have used a broad and rich 
 dataset~\cite{msr17challenge} in our analysis, comprising 1,359 popular projects.
 Other concerns of the study include the possibility that the social factors
 have changed significantly in the past three years, the collapsing of a
 commit's build success to a single successful build and unsuccessful build
 distorted the results, and the possibility that unsuccessful builds were due to
 incorrect test cases and not low quality contributions.\todo{...and?  Something
   like ``future work remains to assess the degree of these threats'' will do.}

@@

\todo{It is not acceptable to only use the shortened venue name.  Also, bilbiography entries are missing venues again; fix it.}

>>>>

74.43\% of the builds in the reduced dataset were successful, and thus a naive
classifer that always guesses ``successful'' would succeed 74.43\% of the time.
To penalize misclassification for
both classes equally, we created a second balanced dataset by randomly 
sub-sampling the successful builds until the two build status were
equal, a process known as downsampling.  We train and present results for both
data sets individually.
\section{Evaluation}
\begin{table*}[ht]
\centering
\begin{tabular}{l||r|r||r|r}
  & \multicolumn{2}{|c||}{Non-Downsampled}  & \multicolumn{2}{|c}{Downsampled} \\
\hline
  & Technical & Technical and Social & Technical & Technical and Social \\
\hline
\textbf{Correctly Classified Instances}&  77.01\% & 81.10\%  & 64.10\% & 76.09\%\\

@@

%\paragraph{External validity} 
Our results might not generalize to 
 other instances outside of the studied cases.  To mitigate this risk, we have used a broad and rich 
 dataset~\cite{msr17challenge} in our analysis, comprising 1,359 popular projects.
 Other concerns of the study include the possibility that the social factors
 have changed significantly in the past three years, the collapsing of a
 commit's build success to a single successful build and unsuccessful build
 distorted the results, and the possibility that unsuccessful builds were due to
 incorrect test cases and not low quality contributions.  Future work will be
 required to investigate the influence of these threats.

@@
